%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    #2 \vspace{-2pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
  \textbf{{\Large Aidan Yang}} & \href{mailto:aidan@cmu.edu}{aidan@cmu.edu}
  \href{https://aidanby.github.io/}{https://aidanby.github.io/} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}



  \resumeSubHeadingListStart
  
  \resumeSubheading
  {Carnegie Mellon University}{Pittsburgh, PA}
  {PhD in Software Engineering}{Expected: 2026}
  \resumeItemListStart
  	\resumeItem{}{Research: program synthesis, program analysis, machine learning}
  \resumeItemListEnd
  
    \resumeSubheading
    {Queen’s University}{Kingston, ON}
      {BEng, Computer Engineering and Mathematics}{2021}
      \resumeItemListStart
      \resumeItem{}{Thesis: modeling the loss function of generative adversarial networks (GANs) with Rényi information measures}
      \resumeItemListEnd
     	
  \resumeSubHeadingListEnd

%-----------Research-----------------
\section{Research}
\resumeSubHeadingListStart

\resumeSubheading
{Carnegie Mellon University}{Pittsburgh, PA}
{Undergraduate Researcher (REUSE). Advisors: Ruben Martins and Claire Le Goues}{Summer 2020}
\resumeItemListStart
\resumeItem{}{Built a program synthesis pipeline for refactoring data-science APIs (e.g., Tensorflow, Pytorch, Dplyr)}
\resumeItem{}{Generated satisfiability modulo theories (SMT) constraints using NLP and deep learning models}
\resumeItemListEnd


\resumeSubheading
{Queen's University}{Kingston, ON}
{Undergraduate Researcher. Advisors: Ying Zou and Ahmed E. Hassan}{May 2018 - May 2020}
\resumeItemListStart
\resumeItem{}{Performed a novel empirical study on 69,851 releases and 67.7 million user reviews for 2,232 apps}
\resumeItem{}
{Built NLP models to establish links between evolving software artifacts achieving 79.8\% accuracy}
\resumeItemListEnd


\resumeSubHeadingListEnd

%-------------------------------------------

%-----------WORK-----------------
\section{Industry}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AMD}{Markham, ON}
      {Software Developer}{Sept 2019 - May 2020}
      \resumeItemListStart
        \resumeItem{}
          {Developed High Dynamic Range (HDR) and Freesync features for GPU drivers }


      \resumeItemListEnd

	\resumeSubheading
		{Queen’s Technology and Media Association}{Kingston, ON}
		{Android Developer}{Sept 2018 - May 2019}
		\resumeItemListStart
		\resumeItem{}
		{Built an Android AR app for student residence furnishing (LucyAR) published on the Google Play Store}
		\resumeItemListEnd


  \resumeSubHeadingListEnd




%--------PUBLICATION------------
\section{Publications}
\resumeSubHeadingListStart

\item{
	{\textbf{An Empirical Study on Release Notes Patterns of Popular Apps in the Google Play Store} \newline
		\underline{Aidan Z.H. Yang}, Safwat Hassan, Ying Zou, Ahmed E. Hassan \newline
	Journal of Empirical Software Engineering (EMSE), 2021
	}
}

\item{
	{\textbf{SOAR: A Synthesis Approach for Data Science API Refactoring} \newline
		Ansong Ni, Daniel Ramos, \underline{Aidan Z.H. Yang}, Ines Lynce, Vasco Manquinho, Ruben Martins, Claire Le Goues\newline
		IEEE International Conference on Software Engineering (ICSE), pp. 112-124, 2021
	}
}

\item{
	{\textbf{SOAR: Synthesis for Open-Source API Refactoring} \newline
		\underline{Aidan Z.H. Yang}\newline
		ACM SIGPLAN International Conference on Systems, Programming, Languages, and Applications: Software for Humanity (SPLASH Companion), pp. 10-12, 2020
	}
}
\item{
	{\textbf{Predicting Co-Changes between Functionality Specifications and Source Code in Behavior Driven Development} \newline
		\underline{Aidan Z.H. Yang}, Daniel Alencar da Costa, Ying Zou \newline
		IEEE/ACM 16th International Conference on Mining Software Repositories (MSR), pp. 534-544, 2019
	}
}
\resumeSubHeadingListEnd

\section{Teaching}
\resumeSubHeadingListStart

\resumeSubheading
{Queen's University}{Kingston, ON}
{TA for Data Structures and Algorithms under Ying Zou}{Winter 2018}
\resumeSubHeadingListEnd
%-------------------------------------------

\section{Presentations}
\resumeSubHeadingListStart
\item{SOAR: Synthesis for Open-Source API Refactoring. Presented at: Systems, Programming, Languages, and Applications: Software for Humanity (SPLASH 2020) Student Research Competition. November 2020}

\item{SOAR: A Synthesis Approach for Data Science API Refactoring. Presented at: Carnegie Mellon University - Institute for Software Research. August 2020}

\item{Predicting Co-Changes between Functionality Specifications and Source Code in Behavior Driven Development. Presented at: International Conference on Mining Software Repositories (MSR). May 2019	
}
\resumeSubHeadingListEnd

%--------AWARDS------------
\section{Awards}
\resumeSubHeadingListStart
\item{Second place at Systems, Programming, Languages, and Applications: Software for Humanity (SPLASH 2020) Student Research Competition}

\item{SIGSOFT CAPS Student Travel Award for ICSE 2019}

\resumeSubHeadingListEnd
%-------------------------------------------


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
        \textbf{Languages}{: Python, C++, R, SQL}
    }
    \item{
        \textbf{Technologies}{: Python PANDAS and Numpy, TensorFlow, PyTorch, PostgreSQL}
    }
 \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
